---
title: "Coursera's Data Science Capstone Final Project (Next Word Predictor)"
author: "Sreenivasulu Parimi"
date: "August 28, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

https://github.com/anzy9/Coursera-Data-Science-Capstone-Final-Project
https://rpubs.com/justusfrantz/capstone
https://rstudio-pubs-static.s3.amazonaws.com/295541_34232d761aeb4e17b7716b67445450bf.html#/
https://rpubs.com/yuyi213/237361
https://rpubs.com/nierhoff/cdsc
https://github.com/mhnierhoff/CapstoneCoursera
http://rstudio-pubs-static.s3.amazonaws.com/239066_d9860715c4b0493cb5412bd26c24ba82.html#/
https://rstudio-pubs-static.s3.amazonaws.com/238817_594713cde25c47f1aaf7f61c7a82b0c7.html#/
https://rstudio-pubs-static.s3.amazonaws.com/236022_dd12fc856c6441c7afeb33067fd656c6.html#/

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

